Estimating Access to Rabies Post-Exposure Prophylaxis in Madagascar

### 2018-12-18 accessPEP.Rmd
with old code + likelihood code

---
title: "Estimating Access to Rabies Post-Exposure Prophylaxis in Madagascar"
author: ""
date: 
output:
  html_document: default
  pdf_document:
    includes:
      in_header: mystyle.sty
  word_document:
    reference_docx: format_docs/word_styles_reference_01.docx
css: style.css
---

## INTRODUCTION

[Start broadly with inequity?]
Inequities in access to healthcare and interventions are a major driver of the burden of disease in human populations. Those most impacted by infectious disease are often those from lower socioeconomic strata and remote populations. Despite the impact of these inequities in shaping disease burden, incorporating these factors into estimations of burden is challenging due to the lack of data resolved to these levels...>

Canine rabies causes an estimated 59,000 human deaths annually. Post-exposure prophylaxis (PEP) prevents fatalities if delivered in a timely manner, however, access to this intervention is highly limited in areas where the disease is endemic. Data on true rabies exposures in humans and incidence in animals is also lacking in most countries. Often, the only data available are numbers of bite victims reporting to health facilities. The majority of rabies burden studies use these data to estimate burden of rabies from probability decision tree frameworks, often with the key assumptions that overall reported bite incidence (i.e. both bites due to non-rabid and rabid animals) are proportional to rabies incidence and that reporting is uniform across space.

The most recent estimation of burden and the impact of PEP used another approach, using transmission dynamic models as the backbone to predict incidence based on level of vaccination coverage and size of the dog population at the national level. Using transmission dynamic models to estimate incidence could improve upon previous studies which may overestimate rabies burden in areas of high reporting and underestimate in areas with low reporting due to the assumption that overall reported bite incidence is proportional to rabies incidence.

Here, we extend this framework to include spatial access to PEP, using bite patient data from 27 clinics in Madagascar, a rabies endemic country that lacks a national strategy for controlling rabies in domestic dogs. Institut Pasteur de Madagascar (IPM) provides PEP at no-cost to the government or to patients that present to 31 clinics across the country. PEP is not available at any other public clinics or through the private sector. Given that rabies is endemic in the country and there is effectively no vaccination of domestic dogs, we use the baseline predictions of incidence from the dynamic model reported in Hampson et al. 2018. We flip the standard decision tree and make the assumption that reported bite incidence reflects access and reporting to PEP rather than differences in rabies incidence, using travel times to clinics as a predictor of bites reported to clinics.

## METHODS

### Bite patient data
We used the database of bite patient forms submitted from 24 ARMC between 2014 - 2017. These were individual patient data forms that were submitted to IPM as frequently as monthly to annually by clinics. Two clinics, the IPM ARMC and the Fianarantsoa ARMC used computer databases from which the data during this period were extracted and merged to the larger database. These data include the administrative district of the bite patient's address. As previous analyses showed likely substantial undersubmission of forms from clinics (*cite baseline data paper*), we calculated the proportion of days of the year for which forms were submitted. We excluded periods with 10 or more consecutive dates with no patient forms and calculated the proportion of days included per year. Figure 1a + 1b?

RIG data?

### GIS Data
We use the global friction surface for 2015 generated by the Malaria Atlas Project ( https://map.ox.ac.uk/research-project/accessibility_to_cities/, Weiss et al. 2015,) and GPS points of clinics to get travel time to the nearest ARMC for the country of Madagascar at a 1 x 1 km scale. We then averaged these to the commune level, using administrative shapefiles available trhough the UN Office for the Coordination of Humanitarian Affairs. For each clinic, we defined the catchment area as all communes for which the clinic was the closest ARMC. Population estimates were taken from the 2015 UN adjusted population projections from World Pop (www.worldpop.org, Linaird et al. 2012) and also aggreagated to the commune level. Figure 2 = networky fig + catchments!

### Model of reported bites as a function of travel time
Excluding any catchments for which there was less than 25% estimated form submission, we calculated the average bite incidence corrected by the annual undersubmission of forms at the district level.

@@

## Preliminary data processing
```{r directory, echo = FALSE, message = FALSE, warning = FALSE, results = 'hide'}
rm(list = ls())
library(knitr)
library(RImagePalette)
library(jpeg)
library(tidyverse)
library(lubridate)
library(magrittr)
library(rgdal)
library(broom)
select <- dplyr::select
knitr::opts_chunk$set(fig.pos = 'h', echo = FALSE, message = FALSE, warning = FALSE, results = 'hide')

### Data
```{r get data}
## read in data
ctar_data <- read.csv("data/SaisieRage_DATA_2018-09-21_1755.csv")
ctar_metadata <- read.csv("data/ctar_metadata.csv")
mada_district <- readOGR("data/MadaGIS/MadaPops.shp")
dist_catchments <- read.csv("output/catchments_district_unmasked.csv", row.names = 1)
names(dist_catchments) <- c("mdg_dis_co", "CTAR", "ttimes_weighted")

## Get color palette from other network fig!
img <- readJPEG("~/Downloads/Dp0j4GNUwAAPPJV.jpeg")
pal <- image_palette(img, 31)
add.alpha <- function(col, alpha=1){
  if(missing(col))
    stop("Please provide a vector of colours.")
  apply(sapply(col, col2rgb)/255, 2, 
                     function(x) 
                       rgb(x[1], x[2], x[3], alpha=alpha))  
}
ctar_metadata$color <- c("#FCC56F","#FFDBE5", "#7A4900", "#CBCDD2", "#0000A6", "#EFF2F1",
                 "#63FFAC", "#B79762", "#004D43", "#8FB0FF", "#997D87", "#FD9C54", "#8362B5",
                 "#578FB0","#5A0007", "#809693", "#D16100", "#1B4400", "#4FC601", "#3B5DFF", 
                 "#4A3B53", "#FF2F80","#61615A", "#BA0900", "#6B7900", "#00C2A0", "#FFAA92",
                 "#FF90C9", "#B903AA", "#FEFFE6", "#E9E9D2")
ctar_metadata$fill <- ctar_metadata$color
ctar_metadata$fill[ctar_metadata$CTAR %in% no_data] <- "#D3D3D3"
ctar_metadata$fill <- add.alpha(ctar_metadata$fill, 0.25)
## Getting ctar district and commune
ctar_metadata$ctar_dist <- mada_district$mdg_dis_co[match(ctar_metadata$District, 
                                                           mada_district$district)]
pts <- SpatialPoints(cbind(ctar_metadata$LONGITUDE, ctar_metadata$LATITUDE), 
                   proj4string = CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
ctar_metadata$ctar_comm <- over(pts, mada_communes)$mdg_cm_

display_palette(ctar_metadata$color)
dist_catchments %>% left_join(select(ctar_metadata, CTAR, exclude, 
                                     color, fill, ctar_dist, LATITUDE, LONGITUDE)) -> dist_catchments
mada_district@data <- left_join(mada_district@data, dist_catchments)
dist_catchments$ctar_in <- ifelse(dist_catchments$mdg_dis_co %in% ctar_metadata$ctar_dist, 1, 0)
```

```{r catchment figure}
## get exposure matrix
ctar_data %>% 
  group_by(district, id_ctar) %>% # group by district and ctar
  summarize(n = n()) -> exp_mat # get count of exposures
dist_points <- cbind(select(mada_district@data,
                            mdg_dis_co), coordinates(mada_district))
names(dist_points)[2:3] <- c("dist_long", "dist_lat")
dist_points %>%
 left_join(select(ctar_metadata, ctar_dist, LATITUDE, LONGITUDE), 
           by = c("mdg_dis_co" = "ctar_dist")) %>%
 mutate(dist_long = coalesce(dist_long, LONGITUDE), 
        dist_lat = coalesce(dist_lat, LATITUDE)) -> dist_points

legend("topleft", c(">100", ">200", ">400", ">800"), title = "Number of total reported bites", 
       text.width = 3, pt.cex = circle_size, col = "grey",  pch = 16, inset = c(0.1, 0.1), lwd = 1.5, bty = "n", xpd = TRUE, y.intersp=2)

exp_mat %>% 
  left_join(select(ctar_metadata, CTAR, id_ctar)) %>%
  left_join(select(dist_catchments, mdg_dis_co, CTAR, exclude), by = c("district" = "mdg_dis_co")) %>%
  group_by(district) %>%
  mutate(prop = n/sum(n),
         catch_match = ifelse(CTAR.x == CTAR.y, 1, 0)) -> catch_check
hist(catch_check$prop)
ggplot(data = catch_check, aes(CTAR.x, district)) + 
  geom_tile(aes(fill = prop)) +
  scale_fill_continuous(type = "viridis", name = "proportion") +
  geom_text(label = catch_check$catch_match)

@@

## Commune level mods
```{r commune matching, echo = FALSE, message = FALSE, warning = FALSE, results = 'hide'}
commune_matching <- read.csv("data/commune_check_CH.csv")
mada_communes <- readOGR("output/communes/communes_extracted.shp")
mada_communes$match <- tolower(str_replace_all(mada_communes$commune,"[^[:graph:]]", "/"))

mada_communes@data %>%
  select(match, mtch_ds, mdg_cm_) %>%
  left_join(commune_matching, .) %>%
  select(name, match, district, mdg_cm_) -> comm_matches

ctar_data$name <- tolower(str_replace_all(ctar_data$commune,"[^[:graph:]]", "/"))
left_join(ctar_data, comm_matches) %>%
  distinct(record_id, .keep_all = TRUE) -> ctar_data

## Looking at proportion matched
ctar_data %>%
  group_by(id_ctar) %>%
  summarise(n = n(), unmatched = sum(is.na(mdg_cm_)),
            prop_matched = unmatched/n) -> ctar_data_matched

ctar_metadata <- merge(ctar_metadata, ctar_data_matched)
ctar_metadata <- ctar_metadata[!is.na(ctar_metadata$id_ctar), ]
ggplot(ctar_metadata, aes(CTAR, prop_matched)) +
  geom_point() +
  coord_flip()  +
  ylab(label = "Proportion of patients matched to commune")
```

```{r }
## Ctar data at commune level
ctar_data %>% 
  filter(excl != 1) %>% # exclude contacts
  mutate_at(vars(starts_with("date")), funs(ymd(.))) %>% # format dates
  group_by(year = year(date_de_consultation), commune = mdg_cm_, id_ctar) %>% # group by year and district
  summarize(n = n()) -> exposures # get count of exposures

comm_catchments <- read.csv("output/catchments_commune_unmasked.csv", row.names = 1)
names(comm_catchments) <- c("mdg_cm_", "CTAR", "ttimes_weighted")
comm_catchments %>% left_join(select(ctar_metadata, CTAR, exclude, 
                                     color, fill, ctar_dist, LATITUDE, LONGITUDE)) -> comm_catchments
mada_communes@data <- left_join(mada_communes@data, comm_catchments)

mada_communes@data %>%
select(commune = mdg_cm_, pop = MDG__201, ttimes_weighted, CTAR, exclude) -> covars
mada_communes$ctar_in <- ifelse(mada_communes$mdg_cm_ %in% ctar_metadata$ctar_comm, 1, 0)

## Catchments with no data
no_data <- c("IPM", "Fianarantsoa", "Ambatomainty", "Ambovombe Androy",
             "Antsiranana", "Mandritsara", "Marolambo", "Nosy be", "Sainte Marie",
             "Taolagnaro", "Tsiroanomandidy", "Vangaindrano")
covars$exclude <- 0
covars$exclude[covars$CTAR %in% no_data] <- 1

exposures %>%
  rename(date = year) %>%
  left_join(covars) %>% # add pop + ttimes + reporting
  left_join(clinic_reporting) %>%   # add reporting by clinic + year
  filter(exclude == 0, prop > 0.25) %>%
  group_by(commune, date) %>%
  mutate(bites = n/prop) %>%
  summarise(bites = sum(bites, na.rm = TRUE)) -> exps_cleaned 
exps_cleaned %>%
  group_by(commune) %>%
  summarise(bites = mean(bites)) %>%
  left_join(covars) -> exps_cleaned

## poisson with total pop as offset
exps_cleaned <- filter(exps_cleaned, ttimes_weighted != "Inf")
mod <- glm(round(bites) ~ ttimes_weighted + offset(log(round(pop))), 
                 data = exps_cleaned, family = poisson)

par(mfrow = c(2, 1), mar = c(4, 4, 1, 1))
plot(exps_cleaned$bites, predict(mod, type = "response"), bty = "l", pch = 20,
     xlab = "Observed bites", ylab = "Predicted bites")
abline(a = 0, b = 1, lty = 2, col = "blue")
legend("topright", col = "blue", legend = "1:1 line", lty = 2, bty = "n", seg.len = 1, 
       inset = c(0.0, -0.1))
plot(exps_cleaned$ttimes_weighted/60, predict(mod, type = "response"), bty = "l", pch = 20,
     xlab = "Travel times (hrs)", ylab = "Bites", col = alpha("blue", 0.7), 
     ylim = c(0, max(exps_cleaned$bites)))
points(exps_cleaned$ttimes_weighted/60, exps_cleaned$bites, bty = "l", pch = 20,
     xlab = "Travel times (hrs)", col = alpha("darkred", 0.7))
legend("topright", col = c(alpha("blue", 0.7), alpha("darkred", 0.7)), legend = c("Predicted", "Observed"), 
       pch = 20, bty = "n")

ctar_data %>% 
  filter(excl != 1) %>% # exclude contacts
  mutate_at(vars(starts_with("date")), funs(ymd(.))) %>% # format dates
  group_by(commune = mdg_cm_, id_ctar) %>% # group by year and district
  summarize(n = n()) ->  exp_mat # get count of exposures

comm_catchments$exclude <- 0
comm_catchments$exclude[comm_catchments$CTAR %in% no_data] <- 1

exp_mat %>% 
  left_join(select(ctar_metadata, CTAR, id_ctar)) %>%
  left_join(select(comm_catchments, mdg_cm_, CTAR, exclude), by = c("commune" = "mdg_cm_")) %>%
  group_by(commune) %>%
  mutate(prop = n/sum(n),
         catch_match = ifelse(CTAR.x == CTAR.y, 1, 0)) -> catch_check
hist(catch_check$prop[catch_check$exclude == 0])
hist(catch_check$prop[catch_check$exclude == 1])

## getting var for ctar in
pts <- SpatialPoints(cbind(ctar_metadata$LONGITUDE, ctar_metadata$LATITUDE), 
                   proj4string = CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
over(pts, mada_communes)$mtch_ds
```

>>>>

---
title: "Estimating Access to Rabies Post-Exposure Prophylaxis in Madagascar"
author: ""
date: 
output:
  html_document: default
  pdf_document:
    includes:
      in_header: mystyle.sty
  word_document:
    reference_docx: format_docs/word_styles_reference_01.docx
css: style.css
---
## Goals
- To estimate burden of rabies in Madagascar using nationally available data from clinics that provide PEP.
- To explore the potential impacts of expanded access to PEP

## Data
- Patient data from 19 ARMC accross the country over four years (2013 - 2017)
  - includes dates and home locations (to the district level) of patient reporting for PEP
- Patient data from Moramanga ARMC over 28 months (Sep 2016 - Dec 2018)
  - includes dates and home locations (to the commune level) of patients reporting for PEP
  - also includes rabies exposure status based on a combination of clinic-based triage and contact
  tracing (Rajeev et al. 2018)
- Travel times estimated from the Malaria Atlas Project's global friction surface for 2015
  - We use the global friction surface for 2015 generated by the Malaria Atlas Project ( https://map.ox.ac.uk/research-project/accessibility_to_cities/, Weiss et al. 2015,) and GPS points of clinics to get travel time to the nearest ARMC for the country of Madagascar at a 1 x 1 km scale. 
  - We then calculated a weighted average by human population to the commune or district level, using administrative shapefiles available trhough the UN Office for the Coordination of Humanitarian Affairs.
  - For each clinic, we defined the catchment area as all communes for which the clinic was the closest ARMC.
- Human population estimates were taken from the 2015 UN adjusted population projections from World Pop (www.worldpop.org, Linaird et al. 2012) and also aggreagated to the designated admin level.

```{r directory, echo = FALSE, message = FALSE, warning = FALSE, results = 'hide'}
rm(list = ls())
library(knitr)
library(RImagePalette)
library(jpeg)
library(tidyverse)
library(lubridate)
library(magrittr)
library(rgdal)
library(broom)
select <- dplyr::select
knitr::opts_chunk$set(fig.pos = 'h', echo = FALSE, message = FALSE, warning = FALSE, results = 'hide')
```

```{r get data}
## read in data
ctar_data <- read.csv("data/SaisieRage_DATA_2018-09-21_1755.csv")
ctar_metadata <- read.csv("data/ctar_metadata.csv")
mada_district <- readOGR("data/MadaGIS/MadaPops.shp")
mada_communes <- readOGR("output/communes/communes_extracted.shp")

## catchment data
dist_catchments <- read.csv("output/catchments_district_unmasked.csv", row.names = 1)
names(dist_catchments) <- c("mdg_dis_co", "CTAR", "ttimes_weighted")
comm_catchments <- read.csv("output/catchments_commune_unmasked.csv", row.names = 1)
names(comm_catchments) <- c("mdg_cm_", "CTAR", "ttimes_weighted")

## Getting ctar district and commune
ctar_metadata$ctar_dist <- mada_district$mdg_dis_co[match(ctar_metadata$District, 
                                                           mada_district$district)]
pts <- SpatialPoints(cbind(ctar_metadata$LONGITUDE, ctar_metadata$LATITUDE), 
                   proj4string = CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
ctar_metadata$ctar_comm <- over(pts, mada_communes)$mdg_cm_
dist_catchments$ctar_in_dist <- ifelse(dist_catchments$mdg_dis_co %in% ctar_metadata$ctar_dist, 1, 0)
comm_catchments$ctar_in_comm <- ifelse(comm_catchments$mdg_cm_ %in% ctar_metadata$ctar_comm, 1, 0)
```

```{r network fig}
## Network fig
## Revise: points = CTAR points with size proportional to number of bites reported, lines to district proportional to the number of bites from that district, outline = by district, communes = polygons shaded by catchments?

## Get color palette from other network fig!
img <- readJPEG("~/Downloads/Dp0j4GNUwAAPPJV.jpeg")
pal <- image_palette(img, 31)
add.alpha <- function(col, alpha=1){
  if(missing(col))
    stop("Please provide a vector of colours.")
  apply(sapply(col, col2rgb)/255, 2, 
                     function(x) 
                       rgb(x[1], x[2], x[3], alpha=alpha))  
}
ctar_metadata$color <- c("#FCC56F","#FFDBE5", "#7A4900", "#CBCDD2", "#0000A6", "#EFF2F1",
                 "#63FFAC", "#B79762", "#004D43", "#8FB0FF", "#997D87", "#FD9C54", "#8362B5",
                 "#578FB0","#5A0007", "#809693", "#D16100", "#1B4400", "#4FC601", "#3B5DFF", 
                 "#4A3B53", "#FF2F80","#61615A", "#BA0900", "#6B7900", "#00C2A0", "#FFAA92",
                 "#FF90C9", "#B903AA", "#FEFFE6", "#E9E9D2")
ctar_metadata$fill <- ctar_metadata$color
ctar_metadata$fill[ctar_metadata$CTAR %in% no_data] <- "#D3D3D3"
ctar_metadata$fill <- add.alpha(ctar_metadata$fill, 0.25)

display_palette(ctar_metadata$color)
dist_catchments %>% left_join(select(ctar_metadata, CTAR, exclude, 
                                     color, fill, ctar_dist, LATITUDE, LONGITUDE)) -> dist_catchments
mada_district@data <- left_join(mada_district@data, dist_catchments)

## get exposure matrix
ctar_data %>% 
  group_by(district, id_ctar) %>% # group by district and ctar
  summarize(n = n()) -> exp_mat # get count of exposures
dist_points <- cbind(select(mada_district@data,
                            mdg_dis_co), coordinates(mada_district))
names(dist_points)[2:3] <- c("dist_long", "dist_lat")
dist_points %>%
 left_join(select(ctar_metadata, ctar_dist, LATITUDE, LONGITUDE), 
           by = c("mdg_dis_co" = "ctar_dist")) %>%
 mutate(dist_long = coalesce(dist_long, LONGITUDE), 
        dist_lat = coalesce(dist_lat, LATITUDE)) -> dist_points

exp_mat %>% 
  left_join(select(ctar_metadata, CTAR, id_ctar)) %>%
  left_join(select(dist_catchments, mdg_dis_co, CTAR, exclude), by = c("district" = "mdg_dis_co")) %>%
  group_by(district) %>%
  mutate(prop = n/sum(n),
         catch_match = ifelse(CTAR.x == CTAR.y, 1, 0)) -> catch_check
hist(catch_check$prop)
ggplot(data = catch_check, aes(CTAR.x, district)) + 
  geom_tile(aes(fill = prop)) +
  scale_fill_continuous(type = "viridis", name = "proportion") +
  geom_text(label = catch_check$catch_match)
```

```{r clinic level reporting}
######### Patient time series
ctar_data %>%
  select(id_ctar, date_de_consultation) %>%
  mutate(date_de_consultation = ymd(date_de_consultation)) %>%
  gather(dose, date_de_consultation, -id_ctar) %>%
  group_by(id_ctar, date_de_consultation) %>%
  summarise(n = n()) -> patient_ts
patient_ts <- patient_ts[!is.na(patient_ts$date_de_consultation), ]
patient_ts$ctar <- ctar_metadata$CTAR[match(patient_ts$id_ctar, ctar_metadata$id_ctar)]
patient_ts <- patient_ts[!is.na(patient_ts$ctar), ]

```{r district level exposures}
## districts that are non-reporter and data not available yet CTAR
mada_district@data %>%
select(district = mdg_dis_co, pop = pop2015adj, ttimes_weighted, CTAR, exclude) -> covars

exposures %>%
  rename(date = year) %>%
  left_join(covars) %>% # add pop + ttimes + reporting
  left_join(clinic_reporting) %>%   # add reporting by clinic + year
  filter(exclude == 0, prop > 0.25) -> exps_cleaned

exps_cleaned %>%
  group_by(district, date) %>%
  mutate(bites = n/prop) %>%
  summarise(bites = sum(bites, na.rm = TRUE)) %>%
  group_by(district) %>%
  summarise(bites = mean(bites)) %>%
  left_join(covars) -> exps_dist

exps_cleaned %>%
  group_by(ctar, date) %>% ## Need to rename CTAR so clear if it's CTAR in catchment vs. ctar of bites...
  mutate(bites = n/prop) %>%
  summarise(bites = sum(bites, na.rm = TRUE)) %>%
  group_by(ctar) %>%
  summarise(bites = mean(bites)) -> exps_ctar

```{r ttimes + pop at commune level}
## Need: weighted ttimes, pop, ctar_in, exclude
comm_catchments %>%
  left_join(select(mada_communes@data, pop = MDG__201, mdg_cm_, district = mtch_ds)) -> comm_covars
comm_covars <- filter(comm_covars, ttimes_weighted != "Inf")
comm_covars %>% 
  left_join(select(mada_district@data, mdg_dis_co, district)) -> comm_data
comm_data$exclude <- dist_catchments$exclude[match(comm_data$mdg_dis_co, dist_catchments$mdg_dis_co)]

## Data to include
nrow(comm_data) - sum(comm_data$exclude)
```

```{r likelihood of observing district data given sum of communes in district}
library()

get.likelihood <- function(commune,district, params) {
  # To test likelihood function
  # commune = comm_data
  # district = exps_dist
  # params = c(1e-6, 0.1)
  B_ttimes <- params[1]
  B_0 <- params[2]
  commune %>%
      filter(exclude == 0) %>%
      group_by(mdg_dis_co) %>%
      mutate(bites = exp(B_ttimes*ttimes_weighted + B_0)*pop) %>%
      summarize(sum_bites = sum(bites)) %>%
      left_join(select(district, district, dist_bites = bites), 
                by = c("mdg_dis_co" = "district")) %>%
      filter(!is.na(dist_bites)) -> sum_bites
  return(-sum(dpois(round(sum_bites$dist_bites), lambda = sum_bites$sum_bites, log = TRUE)))
}

tmp <- optim(par = c(1e-6, 0.1), get.likelihood, district = exps_dist,
             commune = comm_data, hessian = TRUE)
params <- tmp$par
B_ttimes <- params[1]
B_0 <- params[2]

comm_data %>%
      filter(exclude == 0) %>%
      group_by(mdg_dis_co) %>%
      mutate(bites = exp(B_ttimes*ttimes_weighted + B_0)*pop) -> check
plot(check$ttimes_weighted, check$bites)

comm_data %>%
      filter(exclude == 0) %>%
      group_by(mdg_dis_co) %>%
      mutate(bites = exp(B_ttimes*ttimes_weighted + B_0)*pop) %>%
      summarize(sum_bites = sum(bites)) %>%
      left_join(select(district, district, dist_bites = bites), 
                by = c("mdg_dis_co" = "district")) %>%
      filter(!is.na(dist_bites)) -> sum_bites
sum_bites %$% plot(dist_bites, sum_bites)
abline(a = 0, b = 1, col = "blue", lty = 2)

## Model of reported bites as a function of travel time
As bite patient data were only available...

Excluding any catchments for which there was less than 25% estimated form submission, we calculated the average bite incidence corrected by the annual undersubmission of forms at the district level.

@@

@@
